The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-03-14 paper/iphas-dr2.tex
-

A primary motivation for carrying out the survey 
was to enable the discovery 
of new emission-line objects
across the Galactic Plane.
\ha\ in emission is a well-known tracer
for stars in the short-lived pre- or
post-main sequence stages of their evolution,
and hence IPHAS allows larger, deeper
and more statistically robust samples
of such rare objects to be established.
The survey-wide identification and analysis 
of emission-line objects is beyond the scope
of the present work,
but in this section we demonstrate how the
catalogue may be used for this purpose.

>>>>

A primary motivation for carrying out the survey 
was to enable the discovery 
of new emission-line objects
across the Galactic Plane.
\ha\ in emission is a well-known tracer
for stars in the short-lived pre- or
post-main sequence stages of their evolution,
and hence IPHAS allows larger, deeper
and more statistically robust samples
of such rare objects to be established.
The survey-wide identification and analysis 
of emission-line objects is beyond the scope
of the present work and will be the focus
of a forthcoming paper (Barentsen et al, in preparation).
In this section were merely aim to demonstrate
how the catalogue may be used for this purpose.
